Peak area control doc

### 2023-05-25 targeted/targeted_control.Rmd
Clearing out made data in prep for rerun

## Write out quant data
quant_data <- bind_rows(falkor_data, mesotransect_data, mesocenter_data) %>%
  filter(compound_name!="Choline")
write.csv(quant_data, file = "made_data/longdata.csv", row.names = FALSE)
write_csv(quant_data, file = "made_data/all_peaks.csv")
```

>>>>

## Write out quant data
quant_data <- bind_rows(falkor_data, mesotransect_data, mesocenter_data) %>%
  filter(compound_name!="Choline")
write.csv(quant_data, file = "made_data/longdata.csv", row.names = FALSE)
write_csv(quant_data, file = "all_peaks.csv")
```
